\documentclass[11pt,a4paper]{article}

\usepackage[left=0.6in,right=0.6in,top=0.55in,bottom=0.55in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{fontawesome5}
\usepackage[hidelinks]{hyperref}
\usepackage{parskip}
\usepackage{graphicx}
\usepackage{tabularx}

\renewcommand{\baselinestretch}{0.97}

\definecolor{sectionline}{RGB}{25,60,110} 

\titleformat{\section}
{\large\bfseries}
{}{0em}{}[\color{sectionline}\titlerule]

\titlespacing*{\section}{0pt}{4pt}{5pt}

\setlist[itemize]{noitemsep, topsep=1pt, leftmargin=*}

\begin{document}

%==================== HEADER ====================
\begin{center}
  {\Huge \textbf{Zihad Bepari}}\\
  {\Large Software Engineer}\\[6pt]
  {\small
    \faEnvelope\ zihadbepari1139@gmail.com \quad
    \faPhone\ +8801843104250 \\[4pt]
    \faMapMarker\ Tongi, Gazipur, Bangladesh \\[4pt]
    \faLinkedin\ \href{https://www.linkedin.com/in/zihad-bepari-313411329/}{LinkedIn} \quad
    \faGithub\ \href{https://github.com/Zihad-Bepari}{GitHub}
  }
\end{center}

\vspace{6pt}

%==================== PROFILE ====================
\section*{Profile}
{\small
Backend Developer specializing in Golang and Node.js (NestJS), with a strong track record of building secure, scalable, and high-performance backend systems. Experienced in PostgreSQL and advanced database optimization. Skilled in designing and implementing robust authentication systems, real-time communication, payment integrations, and 2FA mechanisms. Strong problem-solving abilities with a competitive programming background, enabling efficient and optimized solutions. Committed to writing clean, maintainable code and delivering reliable, production-grade architectures.
}

%==================== SKILLS ====================
\section*{Technical Skills}

\noindent
\begin{minipage}[t]{0.48\textwidth}
\textbf{Languages:} C, C++, \textbf{Go}, Java, Python \\ 
\textbf{Frontend:} HTML5, CSS3, Bootstrap, \textbf{React} \\
\textbf{Backend:} \textbf{Go}, \textbf{Node.js}, \textbf{NestJS} \\ 
\textbf{Databases:} \textbf{MySQL, PostgreSQL, MongoDB} \\
\end{minipage}
\hfill
\begin{minipage}[t]{0.48\textwidth}
\textbf{Tools:} Git, GitHub, Docker \\
\textbf{Concepts:} OOP, OS, DSA, REST APIs
\end{minipage}

%==================== EXPERIENCE ====================
\section*{Professional Experience}

\textbf{Backend Developer, Luciety, Dhaka} \hfill \textit{Feb 2025 -- Dec 2025}
\begin{itemize}[leftmargin=2em]
    \item Developed scalable backend systems using \textbf{Golang} and \textbf{NestJS}.
    \item Built secure \textbf{RESTful APIs} using \textbf{PostgreSQL} and designed efficient database schemas.
    \item Implemented subscription and payment workflows using \textbf{Stripe}.
    \item Optimized backend performance and collaborated with cross-functional teams.
    \item \textbf{Projects:} 
    \href{https://github.com/Binary-Mindz/johnb-backend-server}{johnb}, 
    \href{https://github.com/mahfuz15/chinasheba-backend/branches}{chinasheba-backend}
\end{itemize}

\textbf{Senior Executive \& Executive, UITS Computer Club (CP Wings)} \hfill \textit{Jan 2024 – Dec 2025}
\begin{itemize}[leftmargin=2em]
    \item Participated in 75+ competitive programming contests.
    \item Mentored 10+ junior students in algorithms and problem-solving.
    \item Conducted programming classes to improve problem-solving skills.
\end{itemize}

%==================== PROJECTS ====================
\section*{Projects}

{\small
\begin{tabular}{p{0.31\textwidth} p{0.64\textwidth}}

\textbf{Independent Voting System} &
A secure voting platform using IoT and blockchain with biometric authentication, preventing double voting and supporting multiple elections.\\
& \textbf{Tech:} Golang, PostgreSQL, IoT, Blockchain \\

\textbf{StoryHub Backend (NestJS)} &
A story-sharing platform with features like posting, liking, commenting, daily limits, and subscription-based premium access.\\
& \textbf{Tech:} NestJS, PostgreSQL, Prisma, JWT \\

\textbf{Chat Application} &
A real-time group chat application supporting text, image, video, and voice messages using Socket.IO.\\
& \textbf{Tech:} NestJS, Socket.IO, PostgreSQL \\

\textbf{Book Selling Platform} &
An online platform for browsing, purchasing, and managing books, with admin control for inventory management.\\
& \textbf{Tech:} React, Node.js, JWT, MongoDB \\

\textbf{Smart Website Locker} &
A browser extension that adds password protection to selected websites and automatically re-locks them after inactivity.\\

\end{tabular}
}

%==================== ACHIEVEMENTS ====================
\section*{Competitive Programming Achievements}
\begin{itemize} [leftmargin=2em]
    \item Skillathon 2025 — \textbf{3rd} (out of 70 teams)
    \item UITS IHFC 2025 — \textbf{3rd} (out of 90+ teams)
    \item UIU Intra University Programming Contest 2025 — Rank 92/130+
    \item UU Intra University Programming Contest 2025 — Rank 86/120+
\end{itemize}

%==================== EDUCATION ====================
\section*{Education}
\textbf{Bachelor of Science in Computer Science} \hfill \textit{Mar 2022 – Feb 2026}\\
University of Information Technology \& Sciences (UITS)

\end{document}